AM205 Project - Traffic Flow Modelling\\ \Large{Microscopic Models of Traffic, Comparing the Intelligent Driver Model (with Adaptive Cruise Control) with the Human Driver Model}

### 2016-12-12 project_paper/paper.tex
added conclusion

\section{TODO}
fuck this to do list, we've done enough. \\
develop a cost function for emissions/energy usage and optimize over that \\
can we find the parameters that will cause a phantom traffic jam?

\section{Discussion}

\section{Conclusion}

>>>>

\section{Conclusion}
The models used within this paper necessarily make many simplifying assumptions, many of which vary somewhat between models. Because of this, it was often difficult to maintain stability of the systems in blended models, as one model may not fully satisfy the assumptions of the other under all parameters. However, within these restrictions, we were still able to construct a series of simulations with stable parameter values and model the reactions of the systems in reasonable ways. We find that in general ACC-controllers are better than human drivers at adapting to and dissipating traffic disturbances and that introducing more self-driving cars in a simplified scenario such as this is likely to improve traffic patterns by reducing the propagation and amplification of traffic waves.
